---
title: "TidyTemplate"
date: 2023-12-21
output: html_document
---

# TidyTuesday

Happy Solstice! Let's celebrate the coming of the light with some data analysis!

I'm going to work through a screenshare with David Robinson, found here:[David Robinson - TidyTuesday Screencast for December 6, 2022](https://www.youtube.com/watch?v=d7uFpxtiXyk). 

I stopped around minute 15 and watched the rest of the screencast without following the coding. 

This code is not my own. 


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
theme_set(theme_light())

```


```{r directories}
code_dir    <- "01_code"
raw_data    <- "02_raw-data"
data_dir    <- "03_clean-data"
results_dir <- "04_results"
```
# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}
a
tt <- tt_load("2022-12-06")

elevators <- tt$elevators %>% 
  janitor::clean_names() %>% 
  filter(longitude > -76) %>% 
  rename_all(str_remove, "^dv_") %>% 
  mutate(floor_to_raw = floor_to, 
         floor_to = is.numeric(floor_to),
         zip_code = str_sub(as.character(na_if(zip_code, 0)), 1, 5),
         floor_to = ifelse(floor_to > 90, NA, floor_to))

  
         
```


```{r}


elevators  %>% 
  arrange(desc(floor_to)) %>% 
  group_by(bin, house_number, street_name, zip_code, borough) %>% 
  summarize(max_floor = max(floor_to, na.rm = TRUE),
            n_elevators = n(),
            .groups = "drop") %>% 
  arrange(desc(max_floor))


```
```{r}

elevators %>% 
  ggplot(aes(longitude, latitude, color = borough)) +
  geom_point()
  



```
```{r}
elevators %>%
  filter(!is.na(floor_to)) %>% 
  mutate(floor_to = as.numeric(floor_to)) %>% 
  ggplot(aes(floor_to)) +
  geom_histogram() +
  scale_x_log10(labels = comma_format(1))



```
we're on Minute 15:02

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = here(results_dir, "My TidyTuesday Plot.png"),
  device = "png")

```
