---
title: "Tidy Tuesday - January 16, 2024"
author: "Adrienne St Clair"
date: "2024-01-19"
output: html_document
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
theme_set(theme_light())
library(here)
library(lubridate)

```
Today I'll be working through the Tidy Tuesday project on my own rather than following a screencast. 

All code is my own. 

```{r directories}
code_dir    <- "01_code"
raw_data    <- "02_raw-data"
data_dir    <- "03_clean-data"
results_dir <- "04_results"
```
# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2024-01-16")

```

Here's background on the data set: [Tidy Tuesday - Polling Places]( https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-01-16/readme.md). 


```{r}
data <- tt[[1]]
```

how do we like the column names that came with the data? 

```{r}
colnames(data)
```
They seem easy enough to work with.   

I looked through the data types and they seem okay for now. I'll consider changing the `state` column to a factor if it seems like it would be useful to be able to drop levels in the future.  

Some states don't have data, as they are primarily vote-by-mail. 
What states are we working with? 
```{r}

data %>%
  select(state) %>% 
  unique() %>% 
  arrange() 

```
How many different types of jurisdiction are there? How many different kinds are found in a single state? 
```{r}
data %>% 
  select(jurisdiction_type) %>% 
  unique()

data %>% 
  group_by(state, jurisdiction_type) %>% 
  summarize(n = n())

```


Looks like we have 39 states. 

The first question that comes to mind is how they compare with polling places per capita. I might be interested in 




